\documentclass[12pt]{book}
\usepackage{fontspec}
\setmainfont{Noto Serif}
\setsansfont{Roboto}
\usepackage{titlesec}
\titleformat{\chapter}[display]
    {\normalfont\Large\bfseries\sffamily}
    {\chaptertitlename\ \thechapter}{1em}{\Huge}
\titleformat{\part}[display]
    {\normalfont\Huge\bfseries\sffamily}
    {\partname\ \thepart}{20pt}{\Huge}
\usepackage{geometry}
\geometry{a4paper, margin=2.5cm}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot[LE]{\thepage} % Left footer on even pages
\fancyfoot[RO]{\thepage} % Right footer on odd pages
\renewcommand{\headrulewidth}{0pt}
\fancypagestyle{plain}{
    \fancyhf{}
    \fancyfoot[C]{\thepage}
    \renewcommand{\headrulewidth}{0pt}
}
\setlength{\headheight}{14.5pt} % Fix fancyhdr warning
\usepackage{microtype} % Reduce overfull hboxes
\usepackage{csquotes} % Already included for \enquote
\usepackage{quoting} % Add this line to define the quoting environment
\usepackage{hyperref}
\usepackage{bookmark} % Fix hyperref bookmark levels and rerunfilecheck
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue
}
\usepackage[english, provide=*]{babel} % Fix babel error

\begin{document}

\begin{titlepage}
    \centering
    \vspace*{3cm}
    {\fontsize{48}{60}\selectfont What Is Your Number\par} % Large, bold title
    \vspace{2cm}
    {\Large Vladimir Sumarov\par} % Author name in a clean size
\end{titlepage}
\clearpage

\chapter*{Content Warning}
This book contains material that may be disturbing or triggering for some readers, including:
\begin{itemize}
    \item Explicit language
    \item Graphic violence
    \item Mature adult themes, including intense combat, interrogation, and sexual content
\end{itemize}
These elements are purely fictional and do not reflect the author’s personal views. Reader discretion is advised.
\clearpage

\tableofcontents
\clearpage

\chapter{Filth and Frost}

\section{Lazy Wave}

In the heart of Moscow, within the Kremlin’s fortified walls, Vladimir Putin sat at the head of a long, polished table. The room was a crypt of shadows, heavy curtains choking out the weak daylight, leaving only the flicker of lamps to carve the faces of his advisors from the gloom. The air hung thick with tension, underscored by the relentless ticking of an antique clock—a reminder that time was slipping. Putin slouched in his chair, a glass of vodka gleaming beside him, untouched, as he half-listened to the stammered reports of his regional governors. The smell of old wood and stale cigarette smoke clung to everything, a relic of decades of whispered threats and broken promises.

One governor, a sweaty hog of a man with a voice like a cornered rat, dared mention rising security threats—vague unrest, whispers of sabotage. Putin cut him off with a lazy wave.

\vspace{0.5em}
\textbf{Putin:} "Your excuses are shit," he snarled, voice a blade through the haze. "Fix the quotas, or I'll bury you myself."

The man flinched, jowls quivering, and Putin smirked, savoring their fear—the way they shrank under his gaze. Power wasn’t just control; it was making them tremble without a move.

The door slammed open, shattering the quiet. A guard stumbled in, pale as the snow outside, his uniform crisp but his eyes wild.

\vspace{0.5em}
\textbf{Guard:} "Sir, there’s been an incident," he said, voice tight. "An attack—near the perimeter. Unknown group."

\textbf{Putin:} "Here?"

The guard nodded, sweat beading.

\vspace{0.5em}
\textbf{Guard:} "Yes, sir. They hit fast—left a message about… numbers."

Putin’s fist crashed onto the table, the vodka glass rattling.

\vspace{0.5em}
\textbf{Putin:} "Numbers? What the hell does that mean?"

\textbf{Guard:} "We don’t know, sir. They vanished before we could lock it down."

Putin shoved his chair back, the scrape a gunshot in the stillness.

\vspace{0.5em}
\textbf{Putin:} "Find them. Drag them to me—alive."

His voice was ice, but a flicker of unease stirred—\emph{numbers?}—some code, some threat he didn’t grasp. He’d crushed rebellions, buried traitors, but this felt off, a shadow he couldn’t pin.

\vspace{0.5em}
\textbf{Putin:} "Lock down the perimeter, double the guards. No one moves unless I say."

The guard saluted, bolting out, and Putin barked,

\vspace{0.5em}
\textbf{Putin:} "Meeting’s over. Get out."

The advisors scrambled, rats fleeing a sinking ship, leaving him alone. He strode to the window, yanking the curtain back. Moscow sprawled below—Soviet relics and gleaming towers, all blanketed in snow. His city. His empire. He wouldn’t let it slip. But that word—\emph{numbers}—gnawed at him, a riddle dropped in his lap. He grabbed the vodka, the burn grounding him, and braced for whatever hunted in the dark.

\vspace{1em}

\section{Shrapnel Hammering}

Vladimir Putin stepped out of the Kremlin’s rear exit, the frigid Moscow night clawing at his face. Snow swirled in vicious gusts, stinging his eyes as he squinted into the dark. His convoy waited—three armored SUVs, engines growling, headlights slicing the blizzard. His tailored black suit bunched under a heavy overcoat as he snapped,

\vspace{0.5em}
\textbf{Putin:} "Move, you lazy fuck," at the driver, sliding into the backseat with a grunt.

The door slammed, muffling the wind, and the convoy rolled out, tires crunching ice.

They hadn’t cleared fifty meters when the night exploded. A deafening roar split the air—the lead car erupted in a fireball, orange and brutal against the snow. Putin’s SUV rocked, shrapnel hammering the windshield like a hailstorm.

\vspace{0.5em}
\textbf{Driver:} "Ambush!" the driver bellowed, swerving as glass spiderwebbed.

Putin ducked, heart slamming, the leather creaking as he braced.

\vspace{0.5em}
\textbf{Putin:} "Who dares this?" he roared, fury and disbelief raw in his throat.

Outside, black cars—sleek, unmarked—screamed from side streets, windows down, rifles spitting fire. Bullets tore through the convoy. A guard’s scream died as a round punched his skull, blood and bone spraying the interior.

\vspace{0.5em}
\textbf{Driver:} "Fuck, fuck, fuck!" the driver cursed, hands white-knuckled, flooring it.

Metal groaned, the SUV fishtailed on ice, and Putin’s hand found the pistol under his jacket—clumsy, untested, a prop now useless.

\vspace{0.5em}
\textbf{Putin:} "Get us out!" he snarled, spittle flecking, his iron facade cracking.

The attackers pressed—a car rammed their flank, jolting him into the door; gunfire stitched the night, a second guard slumping, chest a red ruin. The air reeked of gunpowder and burning rubber, searing his lungs. Through the chaos, a voice cut sharp—a gunner’s shout, distorted but clear:

\vspace{0.5em}
\textbf{Gunner:} "The numbers, old man! Where are they?"

Putin’s mind reeled.

\vspace{0.5em}
\textbf{Putin:} "Numbers?" he muttered, rage tangling with confusion—\emph{What numbers?}

The guard’s warning flashed back—\emph{a message about numbers}—and dread coiled cold in his gut. This wasn’t random; it was targeted, but for what? The SUV swerved, clipping a snowbank; his head cracked the window, pain blurring his vision, blood trickling warm.

\vspace{0.5em}
\textbf{Putin:} "Drive, you idiot!" he bellowed, but the driver’s head lolled—a bullet hole weeping red from his neck.

The car spun, crashing into a lamppost with a bone-jarring crunch. Glass shattered, snow rushed in, gunfire closed tight. Putin clawed at the seatbelt, suit tearing, every breath a gasp. \emph{Me. They’re after me.} His empire unraveled in bullets and flame, and for the first time, fear bit sharper than the cold.

\vspace{1em}

\section{Clawing Boots}

The wrecked SUV smoked in the alley, a tomb for the dead driver and guards. Vladimir Putin crawled out, hands sinking into snow, blood trailing from a gash on his forehead. His suit hung in tatters—jacket shredded, shirt soaked with sweat and red—each breath a rasp burning his lungs. The cold gnawed, but he staggered up, fury outpacing pain.

\vspace{0.5em}
\textbf{Putin:} "Protect me, you fools!" he bellowed at the two surviving guards, their faces pale as they stumbled from the ruin, guns trembling.

They formed a shaky line, boots crunching, breaths fogging the dim alley.

\vspace{0.5em}
\textbf{Guard:} "Move, sir!" one shouted, voice cracking, scanning the dark.

Putin lurched forward, polished shoes skidding on ice, hand braced on a graffiti-smeared wall. The alley was a maze—narrow, slick with frost—gunfire erupting behind, close and sharp. The first guard spun, firing wild—bullets sparked—but a shot took his throat, blood jetting as he collapsed, twitching in the snow.

\vspace{0.5em}
\textbf{Second Guard:} "Keep going!" the second yelled, shoving Putin, his gun barking back.

Another burst—crack, crack—and the guard’s head snapped back, a red hole between his eyes. He dropped, blood pooling dark. Putin stumbled, knees buckling, the pistol lost in the crash a fading hope.

\vspace{0.5em}
\textbf{Putin:} "This isn’t happening," he snarled, voice shaking, hands scraping brick as he hauled upright.

\vspace{0.5em}
\textbf{Putin:} "I am Russia!"

The words rang hollow, drowned by boots closing in. A bullet grazed his arm, ripping his sleeve—he hissed, blood seeping hot between his fingers, staining the snow. He bolted, breath ragged, slipping into Moscow’s backstreets. The storm swallowed sound—only wind and his pounding heart remained. His shoes skidded uselessly; he kicked them off, socks tearing as he ran barefoot over ice and stone, pain lancing through him. Fear drove him harder than pride.

The attackers’ shouts echoed, cold and disciplined:

\vspace{0.5em}
\textbf{Attacker:} "He’s bleeding—track him!"

That word again—\emph{numbers}—clawed back from the ambush, a ghost he couldn’t shake. \emph{What do they want?} Codes? Secrets? Something he didn’t even know he held?

\vspace{0.5em}
\textbf{Putin:} "They’ll pay," he rasped, spit flecking, but the promise weakened—he was alone, unarmed, prey in his own streets.

The alley twisted, shadows deepening, a dead end looming—brick and snow drifts, no way out. His chest heaved, legs trembling as he slowed, cold sinking deep. Boots crunched louder, relentless.

\vspace{0.5em}
\textbf{Putin:} "Fuck," he whispered—a prayer, a curse—turning to face the dark, his reign teetering in Moscow’s filth and frost.

\vspace{1em}

\section{Broken Puppet}

Vladimir Putin stumbled into the dead-end alley, bare feet bleeding into the snow, each step a stab through torn flesh. The brick wall loomed—jagged, iced—under a flickering streetlamp buzzing like a dying fly. His chest heaved, breath clouding, cold clawing his bones. His suit was a ruin—torn, blood-soaked, clinging wet—forehead gash pulsing, red dripping down his face. He turned, back to the brick, facing shadows spilling from the storm: military figures in unmarked black gear, boots crunching with lethal calm.

They closed in, a half-dozen strong, weapons lowered, fists tight—their silence chilling. Putin spat blood.

\vspace{0.5em}
\textbf{Putin:} "You think you can take me? I am Putin!" he snarled, voice cracking, bravado fraying, but he squared his shoulders, fists up like he could fight.

The leader—tall, broad, face scarred—stepped forward.

\vspace{0.5em}
\textbf{Leader:} "What’s your number, old man?" His voice was ice, flat as the Moscow night.

Putin blinked, rage stumbling into confusion.

\vspace{0.5em}
\textbf{Putin:} "What number? What the fuck are you talking about?" he roared, spit flecking.

The leader didn’t flinch—grabbed Putin’s throat, slammed him against the wall with a crunch, air fleeing his lungs.

\vspace{0.5em}
\textbf{Leader:} "The number," he repeated, slow, hard.

\vspace{0.5em}
\textbf{Leader:} "Give it up."

A fist cracked Putin’s jaw—pain exploded, white-hot, copper flooding his mouth.

\vspace{0.5em}
\textbf{Putin:} "I don’t know any fucking number!" he gasped, defiance choking on desperation.

A knee slammed his gut, folding him, ribs creaking. Blows rained—methodical, relentless—a boot smashed his face, splitting his lip; another cracked his cheekbone, vision swimming.

\vspace{0.5em}
\textbf{Putin:} "They’ll pay," he wheezed, words slurring through swollen lips, more plea than threat.

\vspace{0.5em}
\textbf{Putin:} "They’ll pay…"

The leader crouched, yanking Putin’s head back by the hair.

\vspace{0.5em}
\textbf{Leader:} "He doesn’t know. Or won’t say," he muttered to his team, voice flat, disappointed.

Putin’s mind spun—\emph{numbers, numbers}—that damn word haunting every hit. A code? A key? Something buried he didn’t grasp? Dread sank deeper than pain.

\vspace{0.5em}
\textbf{Leader:} "Finish it," the leader said, standing.

They dragged Putin up—legs limp, arms dangling, a broken puppet. A final punch landed—chest, knocking breath into the night. Vision blurred, the alley tilted, and he sagged, consciousness slipping.

\vspace{0.5em}
\textbf{Leader:} "What… is your number?" echoed in his skull, relentless, as darkness took him.

He couldn’t answer—didn’t know—and the snow pressed cold against his face as they hauled him off, a fallen king in a world slipping from his grip.

The attackers moved with purpose—gear whispering of a larger force, maybe a faint insignia glinting, a clipped accent hinting at foreign hands. Putin’s empire lay tattered, power stripped in this bloody alley, the \enquote{number} a mystery heavier than the blows.

\chapter{Roaring Sky}

\section{Raw Knuckles}

Raven stood over the broken heap in the alley, snow dusting the unconscious man’s blood-streaked face—Vladimir Putin, or so they’d thought. The storm howled around him, a bitter Moscow night swallowing the sounds of the fight that had just ended. His black tactical gear was scuffed, knuckles raw and red from the final blow that had dropped the bastard. The air stank of gunpowder and frost, sharp in his lungs as he exhaled a slow, pissed-off breath. His team—three left standing, battered but alert—fanned out, rifles up, securing the narrow killbox of brick and ice.

He knelt, yanking the man’s sleeve back, and pressed a wrist device against the pale skin—a Dimensional Transatron scanner, its red light blinking fast. The screen flared: \textit{No Implant Detected. Identity: Decoy.} “Fuck,” Raven muttered, voice low, gravelly with exhaustion. “Decoy.” He ripped the jacket open, exposing a chest crisscrossed with old scars—no neural chip, no glowing trace of the numbers they’d bled for. Just flesh, useless and fake. He stood, kicking the body once—hard—in the ribs, a dull thud echoing off the walls. “Wrong one. Again.”

His radio crackled, cutting through the wind. “Raven, confirm target,” came the clipped voice of Consortium command. He thumbed the mic, glare fixed on the limp figure. “Negative. We grabbed a damn double. No numbers, no nothing.” A teammate coughed, blood flecking his lips from a stray bullet earlier, leaning against the wall like he might collapse. Another—Vega, wiry and scarred—spat into the snow, muttering, “Fucking waste.” Raven didn’t argue. The alley was a graveyard—two of his own lay dead a block back, guts torn open by the decoy’s guards—and for what? A puppet with Putin’s face.

The scanner blinked again, logging the jump that had led them here—his jump, precise, straight into this shitshow. The Dimensional Transatron had dumped them in this reality, a Moscow with a crimson-tinted Kremlin and too many guns, chasing whispers of the numbers. Those codes—or whatever the hell they were—were the Consortium’s obsession, the key to something bigger, and every miss like this tightened the noose around Raven’s neck. He wiped blood from his knuckles, the sting grounding him, and flexed his hand. “Ditch the body,” he ordered, voice flat. “We’re not done.”

His mind churned, cold and tactical. \textit{Sloppy intel,} he thought, jaw tight. The Consortium was slipping—or someone was feeding them garbage. Every decoy they chased cost lives, time, and sanity, and he was damn tired of it. The numbers weren’t just data—they were a ghost, haunting every jump, every kill. He’d seen the briefings: fragments in powerful heads, maybe tied to a Nexus reality, maybe control over the whole fucking network. But here? Nothing but a corpse that wasn’t even real.

A faint logo glinted on his gear—Consortium, subtle, etched into the fabric. It was a leash, a reminder of who owned him. “Move,” he snapped, turning from the decoy, the snow crunching under his boots. Vega nodded, dragging the body toward a dumpster, while the others reloaded, breaths fogging in the cold. The real Putin was out there, somewhere in this dimension or another, and Raven would find him. Next time, he’d carve the numbers out himself— Consortium be damned—if it meant ending this bloody charade.

\section{Flickering Streetlights}

Raven trudged through the snow, leading his battered team away from the alley’s carnage to a wrecked street a block over. The storm had thickened, fat flakes muffling the distant wail of sirens—Moscow’s chaos swallowing their tracks. His black SUV idled ahead, engine growling, its dented hull a survivor of the earlier firefight. He slammed a fresh magazine into his rifle, the click sharp against the wind, and wiped frost from his breath-fogged visor. “Regroup, now,” he barked, voice cutting through the cold. His three remaining operators moved fast, their gear clinking—Vega, Milo, and the bleeding one, Jax—each a shadow of exhaustion and grit.

“Ditch the body?” Milo asked, spitting a wad of red into the snow—his lip split from a stray elbow in the fight. “Already done,” Vega snapped, wiry frame hunched as he synced a drone to the Transatron network. The device buzzed, its feed flickering with static before locking onto a signal. “Got something,” Vega said, eyes narrowing at the screen. “Second convoy, five klicks out. Moving fast—armed to the teeth.” Raven leaned in, the grainy footage showing sleek black cars cutting through the storm, a faint silhouette in the lead vehicle. Putin. The real one. His gut tightened—another shot, another chance to end this.

“Lock it in,” Raven ordered, voice flat but edged with steel. “Get me eyes on that bastard.” Vega’s hands shook—cold or nerves, didn’t matter—as he tapped coordinates into the drone, its hum rising as it lifted off, vanishing into the blizzard. Jax coughed again, blood streaking his chin, and slumped against the SUV. “Fucking decoys,” he rasped. “How many does he have?” Raven didn’t answer, his silence heavy. Too many, that’s how many—each one a taunt, a middle finger from a man who thought he was untouchable.

He scanned his team, their faces grim under the flickering streetlights. Vega, scarred and twitchy, was their tech—good with machines, shit with patience. Milo, broad and loud, had a temper but could shoot straight. Jax, bleeding and fading, was muscle—loyal, but maybe not for much longer. They were bleeding out, figuratively and not, every jump chipping away at them. The Consortium didn’t care—results mattered, not bodies—and Raven felt the weight of that leash tighter than ever. “Load up,” he said, climbing into the driver’s seat, the leather creaking under his weight. “We’re not losing him again.”

His mind churned, cold and precise. \textit{They’re bleeding us dry with these games,} he thought, fingers flexing on the wheel. The decoy had been perfect—Putin’s face, his voice—until the scanner said otherwise. No implant, no numbers. Just a shell to waste their time. He’d seen the briefings: the numbers were fragments, maybe mnemonic, maybe tech-locked, scattered across realities in the heads of men like Putin. The Consortium wanted them whole—control, power, some Nexus bullshit—and Raven was their hound, sniffing through dimensions for the prize. Doubt gnawed at him—how deep did this go?—but duty shoved it down.

The SUV roared to life, tires gripping the ice as Vega called out, “Drone’s live—two minutes to intercept.” Raven nodded, headlights slicing the dark. “Hold tight,” he growled, flooring it. The real Putin was out there, and this time, Raven wouldn’t settle for a fake. He’d tear through this Moscow—crimson Kremlin and all—and rip the numbers out himself if he had to. The chase was back on, and failure wasn’t an option.


\section{Screeching Tires}

Raven’s SUV roared onto the highway cutting through Moscow’s industrial sprawl, snowbanks flashing past under a crimson-tinted sky. The city’s lights faded into the rearview, swallowed by the storm as his headlights carved a path through the dark. He gripped the wheel, knuckles white, flooring it past rusted factories and skeletal cranes—Vega’s drone feed buzzing on the dashboard screen, tracking the real Putin’s convoy five klicks ahead. “Stay on them,” Raven growled, voice tight, as the speedometer climbed, the engine’s howl drowning out the wind. His team braced—Milo reloading beside him, Vega in the back clutching the drone controls, Jax slumped and bleeding but still breathing.

The chase exploded without warning. A Consortium SUV ahead—backup from the last jump—took a hit, its side erupting in sparks and blood as gunfire ripped through it. The vehicle spun, flipping into a ditch with a sickening crunch, bodies spilling out like rag dolls. “Ambush!” Milo shouted, slamming a mag into his rifle and leaning out the window. Raven swerved, tires screeching on ice, and floored it harder—black cars burst from a side road, Putin’s escorts, their muzzles flashing. Bullets stitched the night, pinging off armor, and Raven barked, “Return fire!” Milo’s rifle roared—two bursts, precise—and a gunner in the lead chase car dropped, his chest a red ruin, tires bursting as the car spun out.

“Got you now, you son of a bitch,” Raven muttered, adrenaline spiking, eyes locked on the sleek, armored car glinting ahead—Putin’s ride, tauntingly close. He leaned out his own window, wind clawing at his face, and squeezed off three shots—surgical, clean—one shattered a pursuer’s windshield, another punched through a driver’s skull, sending the car careening into a snowbank with a fireball bloom. Metal screeched, glass shattered, the air thick with gunpowder and burning rubber. Vega yelled, “Drone’s got him—half a klick!”—but a sniper’s round answered, slicing through the back window and into Vega’s shoulder. His scream cut short as he slumped, blood soaking the seat, the drone controls slipping.

“Fuck!” Raven snarled, swerving as more bullets hammered the hull. Milo twisted, firing blind—emptying a mag into the dark—and clipped another gunner, his body jerking like a puppet before tumbling out. But the enemy’s numbers pressed—two cars flanked them, ramming hard, metal groaning as the SUV shuddered. “Hold it together!” Raven shouted, wrenching the wheel, clipping a snowbank to shake them. Jax coughed, weak, “We’re fucked, boss,” blood bubbling on his lips, but Raven ignored him—focus razor-sharp, every nerve screaming to close the gap.

The highway stretched into a frozen plain, Moscow a distant glow, and Putin’s car loomed closer—its taillights red eyes in the storm. Raven’s shots were surgical, but the bastards were relentless—tires squealed, a chase car rammed again, and Milo grunted as shrapnel grazed his arm, blood flecking the dash. “Air support inbound—watch your six!” crackled through the radio, a Consortium warning too late. Raven glanced back—headlights multiplied, more cars joining the hunt, their engines a chorus of death. \textit{They’re not just protecting him,} he thought, mind racing. \textit{They know what he’s got.} The numbers—whatever they were—drove this madness, and losing them wasn’t an option.

A final burst from Milo took out a driver—car flipped, metal twisting in a shower of sparks—but the cost came fast. A round punched through the side window, catching Jax in the chest; he convulsed, blood exploding across the interior, painting the snow red through the breach. “Jax!” Vega rasped, wounded but alive, clawing for his gun. Raven’s jaw clenched—\textit{Too many gone}—but he kept driving, the real Putin’s car now a shadow in the storm, slipping away. The chase was a meat grinder, and he was running out of meat. “Stay with me,” he growled, voice raw, pushing the SUV to its limit—metal screaming, blood dripping, the numbers haunting every mile.


\section{Rotor Wash}

The highway stretched into a frozen plain, snow whipping across the cracked asphalt as Raven’s SUV roared after Putin’s convoy, now a faint blur in the storm. Moscow’s glow was a memory, the crimson sky bleeding into the dark. His hands gripped the wheel, slick with sweat and Jax’s blood, the engine’s growl a desperate pulse under the chaos. Vega, slumped in the back, clutched his bleeding shoulder, rasping, “He’s pulling away!” Milo, arm grazed and leaking red, reloaded with a grunt—two men left, barely holding. Then the sky roared—a security helicopter thundered overhead, its spotlight blinding, rotor wash kicking up a blizzard of snow.

“Fuck me,” Raven snarled, squinting as bullets rained down, chewing through the road in bursts of dust and sparks. The lead Consortium car—backup from the last jump—took a rocket hit, flipping in a fireball that lit the night orange, bodies shredded in the blast. “Evasive!” he shouted, wrenching the wheel hard—tires screeched, the SUV skidding as metal groaned. Milo leaned out, firing up at the chopper—useless bursts against its armor—but a round punched through his chest, exploding out his back in a spray of gore. He slumped, rifle clattering, blood painting the snow red through the open window.

Raven dove behind the wreckage of their backup car, the heat searing his face as flames licked the twisted hull. “Flank it!” he barked at Vega, who staggered out, dragging a shoulder launcher—last ditch, Consortium issue. Vega braced, fired—the missile streaked, a white-hot scream, but the chopper banked hard, rotor blades thumping, and the shot sailed wide, bursting harmlessly in the snow. “Goddamn it!” Vega rasped, dropping the launcher as bullets stitched the ground around him, kicking up ice and dirt. Raven popped up, Glock blazing—two shots cracked into the chopper’s cockpit, spiderwebbing the glass—but it wasn’t enough.

The air was a cacophony—blades thumped, gunfire cracked, the SUV’s engine ticked faintly in its death throes. Raven’s ears rang, his gear scorched from a near miss, shrapnel biting his leg as he rolled back to cover. The chopper’s guns chewed through asphalt, relentless, a mechanical beast with no mercy. “We’re fucked,” he thought, rage flaring hot. \textit{Outgunned, outmaneuvered.} He’d lost Jax, Milo—half his team in minutes—and Putin was slipping away, the numbers with him. “I’ll rip that pilot’s throat out,” he growled under his breath, the promise a lifeline as death closed in.

A garbled transmission cut through the chaos—his radio, Consortium static: “—numbers secure—abort—” Raven’s gut twisted. \textit{Abort?} Did Putin slip again, or was this a lie to pull them off? The chopper banked, spotlight swinging, and unleashed another volley—bullets tore through the wreckage, pinning him down. Vega crawled beside him, blood soaking his sleeve, eyes wild. “Boss, we gotta—” A round clipped Vega’s thigh, and he screamed, collapsing as red pooled fast. Raven grabbed his collar, dragging him behind a snowbank, the chopper’s roar deafening overhead.

“Hold on,” Raven rasped, voice raw, but the odds were a noose—he was one man against a flying death machine, his team bleeding out in the snow. The spotlight swept again, locking on, and bullets hammered the bank, ice spraying like shrapnel. Putin’s car was gone, swallowed by the storm, and the chopper’s guns didn’t relent. \textit{Too many,} he thought, mind racing. \textit{Too fast.} The numbers—whatever they unlocked—were worth this slaughter, and Raven was the last piece standing. He reloaded, Glock slick with blood, and braced for the endgame, knowing retreat was all he had left.

\section{Fading Flames}

Raven crouched behind the snowbank, the smoldering wreckage of his SUV painting the frozen plain in flickering orange. The helicopter’s roar faded, its spotlight swinging away as it banked hard, pulling back into the storm. Putin’s car had vanished—taillights swallowed by the blizzard, the real bastard slipping through his fingers again. Snow hissed against the flames, the air thick with ash and blood, and Raven staggered to his feet, rifle dangling uselessly at his side. His face stung, shrapnel grazing his cheek, a hot trickle mixing with the frost biting his lungs. “Goddamn waste,” he snarled, kicking the smashed drone—Vega’s last act—its wreckage crunching under his boot.

Vega lay sprawled nearby, thigh torn open, blood pooling dark in the snow. He groaned, weak, fingers twitching toward his dropped pistol. “Boss…” he rasped, voice fading. Raven knelt, checking the pulse—faint, but there—and slung Vega’s arm over his shoulder, hauling him up. “Not losing you too,” he growled, dragging him toward a ditch for cover. Milo and Jax were gone—chests blown apart, bodies cooling in the wreckage—and the weight of it hit like a fist. His team, his brothers, shredded for nothing. The Consortium’s radio buzzed again: “Raven, report.” He thumbed it, voice raw, “Target lost. Team’s gone. Send extraction.”

The plain was a graveyard—twisted metal, burning hulks, snow stained red. Raven’s breath rasped, each inhale a knife of cold, his gear scorched and torn from the chopper’s wrath. He glimpsed Putin’s silhouette in his mind—smug, untouchable, riding away with the numbers locked in his skull. \textit{So damn close,} he thought, exhaustion crashing in. \textit{Next time, I’ll gut him myself.} The numbers gnawed at him—codes, keys, whatever they were—driving this slaughter across dimensions. He’d chased them too long, lost too much, and still didn’t know what they unlocked. Control? Power? A Nexus reality? The Consortium wouldn’t say, and that silence was a chain around his neck.

A faint ping sounded from his wrist device—Consortium signal, another jump queued. He glanced at it, the screen cracked but glowing: \textit{Extraction in route. Prepare for transit.} “Fuck your transit,” he muttered, spitting blood into the snow, but he knew he’d go. Duty—or survival—kept him moving, even as the losses piled up. Vega coughed, fading fast, and Raven tightened his grip, dragging him deeper into the ditch. The chopper was gone, but its echo lingered, a promise of more hell to come. The storm closed in, muffling the world, and Raven sank against the bank, rifle across his lap, watching the flames die out.

His mind churned, bitter and sharp. \textit{What are they hiding?} The numbers weren’t just data—they were a war, bleeding his team dry, and he was the last man standing. Milo’s laugh, Jax’s grunt—ghosts now, haunting the snow. He’d failed them, failed the mission, and the Consortium would demand answers. \textit{Let them try,} he thought, jaw clenching. He’d jump again, hunt again, kill again—until he had Putin’s throat in his hands and the numbers ripped free. The faint hum of an extraction craft broke the silence, lights piercing the storm, and Raven stood, Vega’s weight heavy on his shoulder. The hunt wasn’t over—it was personal now, and he’d burn every reality to ash to finish it.

\chapter{Loud Silence}
\section{Detached Plugs}

Raven stumbled into his sparse apartment, the Dimensional Transatron’s hum still buzzing in his skull like a relentless hangover. He ripped off the headset, wincing as the neural plugs detached with a wet, sickening pop. ``Fucking useless,'' he growled, tossing the gear onto a cluttered table where its cables sprawled like restless snakes. The screen flashed one final taunt---Jump Complete. Target Lost---and he slammed his fist into the wall, drywall cracking under the force. His knuckles bled, the sharp sting a fleeting relief from the deep ache in his bones.

He stripped off his blood-streaked fatigues, exposing a body etched with scars---mementos of jump mishaps, knife fights, and bullet grazes, each mark a testament to survival, each a burden. The apartment was a dump---Consortium didn’t waste credits on luxury---just a bed, a kitchenette, and the hulking Transatron rig looming in the corner like a predator. He snatched a half-empty bottle of cheap vodka from the counter, the glass cold against his calloused palm, and poured a shot, downing it in one swift motion. The burn slid down his throat but did nothing to ease the exhaustion or silence the ghosts---Milo’s scream, Jax’s blood, Vega’s fading pulse echoing in his mind. \textit{Team’s dead, numbers gone,} he thought, jaw clenched. \textit{Consortium’ll have my head.}

His wrist device blinked---an alert for another jump, another hunt. He ignored it, pouring a second shot, the vodka sloshing over his fingers. The Transatron’s toll was merciless---each dimension leap shredded his nerves, left him a hollow shell---but the Consortium didn’t give a damn. Results trumped bodies, and he was running on empty. \textit{I need a break,} he admitted to himself, the thought bitter as bile, \textit{or I’ll break.} He sank onto the bed, boots still laced, and stared at the ceiling, its cracks mirroring the fractures in his mind. The ``numbers'' obsessed him---fragments locked in Putin’s skull, keys to some Nexus reality, maybe dominion over the entire network. He didn’t fully understand, didn’t care---just wanted the job finished.

A faded photo on the counter snagged his gaze---his old team, grinning like fools after a successful jump. Vega, unscarred, Jax, alive and laughing. \textit{Gone now,} he thought, throat tightening. The Consortium’s leash tightened with every failure, every loss. He’d signed up to hunt, not to carry the dead. Another gulp of vodka scorched his throat, but it couldn’t wash away the questions---how deep did this conspiracy run? What were the numbers truly worth? The rig hummed faintly, a Consortium alert pulsing---more jumps, more blood. He crushed the glass in his hand, shards biting into his flesh, and let the pain ground him. \textit{One more,} he vowed, \textit{then I’m out.} A lie, and he knew it.

Raven hauled himself up, unsteady, and grabbed his worn leather jacket---a civilian disguise. \textit{Need air. Need noise.} The apartment’s silence felt like a tomb, and he wasn’t ready to be buried. He’d hit the dive bar, drown the day in cheap liquor and loud music, maybe find a distraction with a pulse and a smirk. Sasha’s face flickered in his mind---bold, reckless, a walking hazard---but damn if he didn’t crave it. He stepped out, boots thudding on concrete stairs, the city’s distant hum offering a shred of escape. The Transatron’s glow lingered in his vision, a cruel reminder that peace was a fleeting illusion, and the hunt was far from over.

\section{Grayish Stew}

Raven stood over the kitchenette’s chipped sink, the flickering bulb overhead casting jagged shadows across his scarred back. The apartment’s silence pressed in, broken only by the faint hum of the Transatron rig in the corner—a constant, nagging reminder of the shitshow he’d just survived. He peeled off the last of his gear, letting it thud to the floor—blood-streaked fatigues, a cracked wrist device—and flexed his hands, knuckles still raw from the drywall. A pot of grayish stew sat cold on the counter, leftovers from who-knows-when. He scooped it into a bowl, reheated it in the microwave’s stuttering glow, and ate standing up, spoon scraping metal. The stuff was cold in the middle, tasteless as ash, but he didn’t care—fuel was fuel.

“Food’s shit,” he muttered, voice rough, scraping the last bite. “Better than stewing here—literally.” The thought landed flat, no humor in it, just the dull ache of a man too tired to laugh. He rinsed the bowl, water splashing over his hands, and caught his reflection in a cracked mirror above the sink—eyes sunken, stubble thick, a face that looked older than his years. The scars on his torso gleamed under the light—jagged lines from a jump gone wrong, a bullet graze from some forgotten reality. Each one a story, each one a weight. He grabbed a worn leather jacket from a chair, shrugging it on over a plain shirt—civilian wear, a thin mask to hide the killer underneath.

The apartment was bare—Consortium didn’t pay for comfort, just results. A single bed, unmade, a table littered with gear, and that damn rig, its cables snaking like veins. A photo on the counter snagged his eye again—his old team, frozen in a moment before the numbers turned everything to blood. Jax’s grin, Vega’s cocky tilt—ghosts now, haunting him with every glance. He turned away, jaw tight. *Can’t sit here,* he thought, the silence too loud, the walls too close. *Need air. Need noise.* The bar was calling—smoke, liquor, a chance to drown the day before it drowned him.

He laced his boots, the thud of leather on tile a steady rhythm, and grabbed a flask from a drawer—dented, half-full of something stronger than the vodka. A quick swig burned his throat, steadying the tremor in his hands—jump fatigue, Consortium’s gift that kept on giving. *Another jump, another fuck-up,* he thought, the bitter taste lingering. The numbers danced in his head—elusive, deadly, a puzzle he couldn’t crack. Putin had them, or some version of him did, and Raven was the hound sent to fetch, no questions asked. Doubt flickered—*What am I even chasing?*—but he shoved it down, habit as much as duty.

The city waited outside, a neon-lit sprawl of crumbling towers and flickering signs, its hum filtering through the cracked window. He stepped to the door, boots heavy on the concrete stairs, the jacket creaking as he moved. The bar wasn’t far—a dive where the drinks were cheap and the company didn’t ask questions. Maybe Sasha would be there, her bold laugh cutting through the haze, her reckless edge a match for his own. *Trouble,* he thought, a faint smirk tugging his lips, *but the good kind.* He needed it—something real, something alive—before the Consortium dragged him back into the void. The door slammed shut behind him, the Transatron’s hum fading, and he descended into the night, a shadow seeking respite in a world that offered none.

\section{Smoky Haze}

Raven pushed through the dive bar’s warped door, the smoky haze hitting him like a fist—thick with cheap booze, sweat, and the tang of desperation. The jukebox crooned some mournful tune, its notes warring with the low hum of slurred voices and clinking glasses. He slumped onto a stool at the chipped bar, the wood sticky under his elbows, and nodded at the bartender—a grizzled bastard with a missing tooth. “Usual,” Raven grunted, voice rough from vodka and fatigue. A glass of the clear stuff slid over, cold and sharp, and he downed half in one gulp, the burn a welcome jolt against the day’s weight.

The place was a pit—patrons hunched over tables, faces carved with hard lives, their laughter brittle and fleeting. Neon flickered outside, casting red streaks through grimy windows, the city’s pulse a dull throb beyond the walls. Raven scanned the room, habit more than interest, until a teammate lumbered over—Jax, not the dead one, but another burly grunt named after the same dumb luck. “Decoy again,” Jax muttered, sliding onto the next stool, his beer sloshing. “Boss is raging—says we’re fucked if we don’t deliver soon.” Raven grunted, staring into his glass. “They always are.”

Jax leaned closer, voice dropping. “Jumps are frying us, man. Numbers better be worth it—lost three last month to glitches alone.” Raven’s jaw tightened—\textit{glitches}, Consortium’s polite word for brains scrambled by bad jumps, bodies left twitching in some nowhere reality. He didn’t reply, just sipped, letting the vodka numb the ache of Milo’s scream still ringing in his skull. Then he saw her—Sasha Volkov, leaning against the bar a few stools down, sharp-eyed and smirking like she owned the damn place. Leather jacket, boots scuffed from kicking something—or someone—her dark hair spilling wild over her shoulders.

“You look like you’ve seen hell,” she called, voice cutting through the din, playful but edged. Raven met her gaze, her confidence slicing through the haze like a blade. “Lived it,” he shot back, a faint smirk tugging his lips—first real one all day. She sauntered over, hips swaying just enough to draw eyes, and leaned on the bar beside him, sipping something dark from a chipped glass. “Buy me a drink, hero?” she teased, nails tapping the rim, her stare bold and unyielding. He nodded at the bartender—“Her next one’s on me”—and turned to her, sizing her up. \textit{Trouble on legs,} he thought, the good kind stirring something he hadn’t felt since the last jump didn’t end in blood.

“Rough day?” she asked, head tilting, curiosity glinting in her eyes. “Rough life,” he said, voice low, letting the weight hang between them. She laughed—sharp, unafraid—and it hit him like a shot of adrenaline. “Heard you chase bad guys across… what, dimensions?” she said, half-joking, fishing maybe, but close enough to make him pause. “Something like that,” he replied, smirk deepening, not giving her the full truth—not yet. Jax snorted beside him, muttering, “Understatement,” but Raven waved him off, focus narrowing to her.

Their knees brushed under the bar, a spark igniting in the cramped space—her jeans rough against his, heat cutting through the cold he’d carried in. “So,” she pressed, leaning closer, breath warm with liquor, “you gonna prove you’re not all talk, or just brood into that glass?” Raven’s pulse kicked up, a rare flicker of something alive beneath the exhaustion. “Careful what you ask for,” he said, meeting her challenge, voice a gravelly promise. She grinned, fearless, and finished her drink, the glass clinking hard on the bar. “Try me,” she shot back, eyes locked on his.

Jax chuckled, shaking his head—“You’re fucked, mate”—and lumbered off, leaving them alone in their bubble of tension. \textit{She’s not scared off,} Raven thought, curiosity stirring. \textit{Rare.} Most saw the scars, the edge, and ran—Sasha leaned into it, a thrill-seeker with no clue what she was poking. The numbers, the jumps, the blood—they faded for a moment, drowned by her laugh, her heat. “Finish that,” she said, nodding at his vodka, “and let’s get out of here.” The bar’s noise dulled, the city’s hum a distant lure, and Raven downed the rest, the burn sealing the deal. He needed this—her—more than he’d admit, a lifeline before the Consortium dragged him back to hell.

\section{Creaking Leather}

Raven slid into the bar’s corner booth with Sasha, the shadowy nook a cramped refuge from the dive’s clamor. The crowd had thinned, leaving a haze of smoke and muted voices, the jukebox’s wail fading to a low growl. She settled across from him, her leather jacket creaking, drinks in hand—his vodka, her something dark and bitter. The booth’s worn upholstery scratched at his jeans, but he barely noticed, his focus narrowing to her. She leaned close, smirking, her knee brushing his under the table—a deliberate graze, rough denim against rougher denim, sparking heat through the fatigue clinging to his bones.

“So,” Sasha said, voice low and teasing, “you chase bad guys across dimensions, huh?” She swirled her glass, ice clinking, her eyes glinting with mischief. Raven smirked back, leaning in just enough to feel her breath—warm, laced with liquor. “Something like that,” he replied, keeping it vague, the truth too bloody to spill here. Her boldness hooked him, a lifeline pulling him from the wreckage of Milo’s scream, Jax’s blood. “Sounds like a hell of a gig,” she pressed, her foot nudging his calf now, testing him. “Prove you’re not all talk, soldier boy.”

He met her gaze, steady and unyielding, the bar’s dim light catching the scars on his knuckles. “Careful what you ask for,” he said, voice a gravelly edge, half-warning, half-promise. Her grin widened—fearless, reckless—and she downed her drink, the glass thudding hard on the table. “I can handle it,” she shot back, leaning closer, her hand grazing his on the tabletop—smooth against rough, a jolt that kicked his pulse up. \textit{She’s pushing,} he thought, desire flaring past caution. \textit{I’m biting.} The day’s hell—jumps, death, the numbers—slid away, drowned by her heat, her challenge.

Their fingers tangled briefly, a clumsy spark, and he felt the calluses on her palm—proof she wasn’t soft, wasn’t fragile. “You’re trouble,” he muttered, smirk deepening, the vodka’s burn still sharp on his tongue. “Good kind, maybe.” She laughed—sharp, alive—and pulled her hand back, but the air stayed electric, thick with unspoken stakes. “Finish that,” she said, nodding at his glass, “and let’s get out of here.” The bartender winked from across the room—Raven’s done this dance before—but this felt different, heavier, a need clawing up from the pit of him.

He downed the vodka, the last swallow searing his throat, and stood, her shadow rising with him. Her boots scuffed the floor as she followed, close enough that her jacket brushed his arm, leather on leather. \textit{Fuck it,} he thought, the day’s weight crashing into a hunger he couldn’t ignore. “Where to?” he asked, voice low, already knowing the answer. “Your place,” she said, bold as hell, stepping into his space like she belonged there. The bar’s noise faded, the city’s hum a siren call beyond the door, and he nodded—once, sharp—leading her out.

The night swallowed them, neon flickering overhead, the cold biting at his face as they stepped into the sprawl. Her hand found his again, gripping tight, and he didn’t pull away—needed it, needed her, more than he’d admit. The Consortium, the numbers, the blood—they’d wait. For now, it was just them, two sparks ready to ignite, and Raven let himself fall into it, a fleeting escape before the hunt dragged him back.

\section{Messy Bed}

Raven crashed through his apartment door with Sasha, the lock barely clicking shut before their lips clashed—hard, hungry, a collision of need and heat. The city’s hum filtered through cracked windows, a distant pulse against the Transatron’s faint glow casting eerie shadows across the messy bed. She yanked his jacket off, nails digging into his scarred back as he lifted her onto the kitchenette counter, the wood creaking under her weight. “Fuck,” he growled, voice raw, hands gripping her hips as she arched into him, her leather jacket hitting the floor with a thud. Clothes followed—jeans unzipped in a tangle, her shirt torn over her head, his briefs kicked aside—scattered like wreckage in their wake.

She tasted of liquor and smoke, her tongue bold against his, and he matched her—rough, unyielding, teeth grazing her lip until she gasped. His hands slid under her thighs, pulling her closer, skin slick with sweat as the counter rocked beneath them. “Harder,” she demanded, voice a husky edge, her legs wrapping tight around his waist. He obliged, thrusting deep, a rhythm that shook the room—grunts and gasps syncing in ragged bursts. Her nails raked his shoulders, drawing red lines over old scars, and he hissed, the sting fueling him, drowning the ghosts of Milo, Jax, the numbers in a flood of now.

The bed came next—he carried her there, stumbling over gear, dropping her onto the tangled sheets. She laughed—sharp, wild—as he pinned her wrists, her body yielding but fighting back, a dance of push and pull. “You’re a bastard,” she breathed, grinning, her hair a dark halo against the pillow. “You love it,” he shot back, voice gravelly, sinking into her again—slower now, deliberate, each move a release of the day’s hell. Sweat beaded on his brow, dripping onto her chest, and she arched, meeting him, her breath hitching as the pace built, relentless, real.

Skin slapped skin, the air thick with their heat—messy, alive, a stark contrast to the cold precision of jumps and kills. He gripped her hips, calluses rough against her smoothness, and she moaned, loud and unashamed, the sound cutting through the apartment’s gloom. “Don’t stop,” she rasped, hands breaking free to claw his back, urging him on. He didn’t—couldn’t—lost in her, in this, the world shrinking to the creak of the bed, the slick of their bodies, the raw edge of release clawing closer. \textit{This—her—it’s real,} he thought, relief flooding through the haze. \textit{Not the jumps, not the blood.}

They hit the peak together—she shuddered beneath him, a cry tearing from her throat, and he followed, a low groan spilling out as he collapsed, spent, beside her. The bed sagged, springs whining, their breaths heaving in sync as the Transatron’s hum crept back into focus. She rolled onto her side, sweat-slicked and grinning, propping her head on one hand. “Hell of a day, huh?” she said, voice soft but sharp, cutting through the afterglow. He nodded, winded, a faint smirk tugging his lips. “Hell of a night.”

His chest ached—not just from exertion, but from something deeper, a crack in the armor he’d worn too long. She was trouble, reckless, a civilian with no clue what he carried—Putin’s numbers, the Consortium’s leash, the bodies piling up—but right now, she was his anchor. He traced a finger along her arm, her skin warm under his touch, and let himself linger in it, the first peace he’d felt in months. \textit{Need this more than I thought,} he admitted, the thought heavy, unguarded.

The Transatron’s hum grew louder, insistent, its glow pulsing faintly across the room—Consortium’s call, always waiting. Sasha’s eyes flicked to it, curious, but she didn’t ask—not yet. She curled closer, her leg draping over his, and he let her, their sweat mingling as they drifted, the city’s hum a lullaby. Exhaustion pulled at him, the day’s weight crashing back, but her warmth held it off—just for now. The rig beeped once, a warning he ignored, and they sank into silence, a fragile truce before her fate—and his—shifted gears.

\chapter{Screaming Static}

\section{Oversized Shirt}

Sasha Volkov stirred awake in Raven’s bed, the tangled sheets warm against her bare legs, a faint grin tugging her lips at the memory of last night—wild, raw, a hell of a ride. Gray light seeped through cracked blinds, painting the sparse apartment in muted streaks. She stretched, arms popping, and rolled over, expecting his scarred bulk beside her. Nothing—just a dent in the pillow and a scribbled note: \textit{Thanks for the night—work called. Stay, eat, back soon.} “Guess I wore him out,” she muttered, voice husky with sleep, smirking as she swung her legs off the bed.

The floor was cold under her feet, concrete biting through the haze of her buzz. She snagged his oversized shirt from the floor—smelling of him, sweat and leather—and pulled it on, the hem brushing her thighs. The place was a mess—gear strewn across a table, the Transatron rig looming in the corner like some sci-fi beast, its cables snaking over the clutter. She padded to the kitchenette, brew in mind, and flicked on a dented coffee maker. Black, bitter liquid sputtered out, stale as hell, but she sipped it anyway, leaning against the counter, the mug’s heat a small comfort in her hands.

“Guy’s a mystery,” she said to the empty room, eyes drifting over his stuff—hot as sin, sure, but layered with secrets. A photo caught her eye—Raven with a crew, all grins, no scars yet. *Old team,* she guessed, curiosity prickling. Then the Transatron snagged her full attention—sleek, glowing, a puzzle begging to be cracked. “What’s with all this tech?” she murmured, stepping closer, the hum vibrating faintly under her bare feet. He’d dodged her dimension talk at the bar, but that rig? It screamed \textit{badass simulator}, and she was itching to find out.

She rifled through a drawer—flasks, a knife, junk—grinning at the chaos of him. “He said dimensions,” she mused, voice low, replaying his smirk, his vague “something like that.” Her fingers brushed a book on cryptography, dog-eared and worn—*nerd shit,* she thought, but it fueled the fire. The coffee went down fast, bitter and grounding, and she prowled closer to the rig, its lights blinking like a dare. *Bet it’s how he unwinds,* she decided, imagining him strapped in, chasing thrills across some virtual hellscape. Her pulse kicked up—\textit{Why not me?}

The note’s casual tone—*Stay, eat*—felt off, too calm for a guy like him. She glanced at it again, tossed on the pillow, and shrugged. *Work called, my ass,* she thought, a thrill-seeker’s grin spreading. The Transatron’s glow pulled her in, a siren call she couldn’t resist. She’d played VR before—dumb arcade stuff—but this? This was next-level, and Raven’s edge made it irresistible. “Let’s see what you’re hiding, soldier boy,” she said, voice bright with mischief, already plotting her dive. The city hummed outside, a faint thud of boots echoing somewhere below—trouble, maybe, but she didn’t hear it yet, too caught in the rush of what came next.

\section{Stale Coffee}

Sasha prowled Raven’s apartment, coffee mug still warm in her hand, the Transatron’s hum a siren song tugging her closer. The living area was a chaos of his life—gear piled on a table, books on cryptography scattered like fallen soldiers, their pages bent and stained. She smirked, flipping a photo of his old team—Raven, younger, grinning with guys she’d never meet. “Hotshot with a past,” she muttered, voice low, setting it down to dig further. Her fingers brushed a dented flask, half-full of something sharp—she unscrewed it, took a swig, and winced as it burned. “Man’s got taste,” she said, wiping her mouth, the buzz fueling her nosy streak.

The Transatron dominated the room, a sleek beast of metal and wires, its glowing interface pulsing like it was alive. “What’s this, VR on steroids?” she mused, stepping closer, bare feet scuffing the cold floor. Raven’s dodge at the bar—\textit{something like that}—echoed in her head, and she grinned, wide and wicked. “Let’s play, soldier boy.” She set the mug down, splashing stale coffee, and powered the rig on—lights flared, a low whine building, the air crackling with static. Her pulse jumped—\textit{Holy shit, this is gonna rock}—and she giggled, a thrill-seeker’s glee bubbling up.

She climbed into the rig, the seat hard against her thighs, and strapped in—buckles snapping tight, cables snagging her wild hair. The headset loomed, heavy and slick; she pulled it on, grunting as it settled, neural plugs clicking into place with a faint jolt. “Ow, fancy,” she quipped, shaking off the sting. A screen blinked to life: \textit{Select Jump: Moscow-7.} She tilted her head, still in Raven’s shirt, jeans forgotten in the rush. “Moscow-7? Sounds fun,” she said, shrugging—\textit{What’s the worst that could happen?}—and hit enter, the command a spark to her reckless fire.

The rig whirred louder, vibrations rattling her bones, and a warning flickered—\textit{Unauthorized Access}—in red across the screen. “Pfft, buzzkill,” she muttered, jabbing enter again, ignoring it like a kid dodging rules. The whine spiked, a rush of static flooding her ears, and she gripped the straps, laughing through the nerves. “He’s got secrets,” she thought, excitement drowning caution. \textit{Bet this is how he unwinds—hope it’s got killer graphics.} The room blurred, the apartment’s mess fading as the Transatron kicked in, a “tearing” sensation clawing at her gut—sharp, wild, like nothing she’d felt.

Her stomach lurched, coffee threatening to come back up, but she swallowed it down, grinning through the daze. “Here we go!” she whooped, voice bright, oblivious to the real stakes snapping into place. The rig’s lights pulsed faster, a heartbeat she didn’t clock as trouble—\textit{Consortium security my ass,} she’d have scoffed if she knew. Outside, the city’s hum droned on, boots thudding faintly below—Liang’s team, closing in—but she was too caught in the rush, the thrill of cracking Raven’s world wide open. The screen flared, coordinates locking, and she braced herself, a civilian about to tumble into hell with a laugh on her lips.

\section{Rumbling Car}

The jump hit Sasha like a freight train—a flood of static screamed in her ears, colors exploding behind her eyes, then a “tearing” sensation ripped through her gut, sharp and wild. She landed hard, sprawled in the driver’s seat of a rumbling car, snow pelting a cracked windshield. “Holy shit,” she gasped, laughing through the daze, head spinning as she gripped the wheel—\textit{That’s immersive!} The air stank of oil and frost, a terminal beside her blinking coordinates: \textit{Target Location: Sector 12. Neutralize threats.} Guns rested on the seat—a pistol, sleek and cold—and she snatched one up, grinning wide. “Game on!”

She floored the gas, the car lurching forward with a roar, tires screeching on ice as she weaved through a militarized Moscow—crimson skies bleeding over fortified streets, buildings bristling with razor wire. “This is next-level,” she whooped, voice bright, oblivious to the real blood waiting. The dashboard vibrated under her hands, the armored beast growling as she swerved past checkpoints—guards in drab coats shouting, rifles swinging her way. She laughed again, steering with one hand, pistol dangling in the other. “Raven’s a genius—best VR ever!”

A guard stepped into her path, weapon raised—\textit{First level, huh?}—and she squeezed the trigger, more instinct than aim. The shot cracked, loud and real; the guard’s chest bloomed red, and he dropped with a surprised grunt, sprawling in the snow. “Whoa,” Sasha breathed, eyes wide, a giggle bubbling up. “Realistic as fuck!” She floored it harder, adrenaline spiking, the car fishtailing through a turn—metal groaned, snow sprayed, and she spotted more guards ahead, their shouts drowned by the engine’s howl.

“Take two!” she yelled, leaning out the window, wind clawing her hair as she fired again—pop, pop—two more dropped, blood staining the white in stark splashes. “Suckers!” she crowed, pride swelling, the recoil bruising her hand but damn if it didn’t feel good. The terminal beeped—\textit{Sector 12: 500 meters}—and she grinned, weaving past a barricade, tires crunching over debris. “Gonna rack up points like a pro,” she thought, thrill overriding the faint churn in her gut—\textit{Kinda gory, but whatever.} This was her playground, and she was winning.

The streets twisted, crimson light glinting off steel and ice, a warlike hum pulsing through the city—Moscow-7, a reality she didn’t clock as real. A radio crackled: “Operator, confirm status,” a voice sharp and clipped. Sasha smirked, assuming AI—\textit{Cool touch}—and shouted back, “Kicking ass, buddy!” No reply, just static, and she shrugged, too caught in the rush to care. Ahead, a compound loomed—Sector 12, floodlights cutting the dark, guards swarming like ants. She screeched to a stop, snow drifting around her, and hopped out, pistol cocked, boots crunching ice. “Boss level time,” she muttered, eyes gleaming.

A distant figure moved toward a convoy—tailored coat, a limp—Putin, or some badass stand-in, her “final boss.” She lined up a shot, finger twitching, heart pounding with glee. “Gotcha,” she whispered, but a guard yelled, “She’s not one of ours!”—voice too human, too panicked. Bullets whizzed past, pinging the car, and she ducked, laughing through the shock. “Nice try!” she called, popping up to fire back—one crumpled, blood spraying, his scream cut short. \textit{Too easy,} she thought, pride surging, though a flicker of doubt crept in—\textit{This shit’s intense.}

The compound’s chaos swallowed her—gunfire, shouts, the car’s engine ticking behind her. She darted forward, snow stinging her face, Raven’s shirt flapping loose, no clue she’d stumbled into a real hunt. The terminal blinked—\textit{Neutralize threats: 3 remaining}—and she took it as a score, not a death tally. “Raven’s got nothing on me,” she thought, grinning, the thrill drowning that nagging itch—\textit{Why’s it feel so real?}—as she charged deeper, a civilian playing warrior in a war she didn’t understand.

\section{Slick Grip}

Sasha crouched behind the car in Sector 12, snow swirling around her, the compound’s floodlights slicing through the crimson-tinged dark. Razor wire glinted atop concrete walls, guards patrolling with rifles slung—her “level” alive with threats. She gripped the pistol, hand bruised from recoil, and peeked out, Raven’s oversized shirt flapping in the wind. “Time to shine,” she muttered, grinning, the terminal’s order—\textit{Neutralize threats}—a score to beat. She popped up, aimed at a guard pacing near a gate, and fired—hesitant at first, the shot cracking loud. His head jerked, blood spraying as he crumpled, a rag doll in the snow. “Oops,” she laughed, “that guy’s super dead!”

The thrill hit hard—\textit{This is too good}—and she shook off the jitters, diving in with gusto. Another guard spun toward her, shouting, rifle swinging—she squeezed off two rounds, chest shots, and he staggered, dropping with a wet thud, red pooling stark against white. “Take that, suckers!” she whooped, voice bright, adrenaline pumping as she darted forward, boots crunching ice. A third loomed, bigger, barking orders—she aimed wild, bullet clipping his shoulder, then steadied and fired again, punching through his throat. Blood jetted, his gurgle fading fast, and she pumped a fist. “Three down—high score, baby!”

The compound buzzed—shouts, boots pounding, a chaos she owned. She sprinted past the bodies, snow stinging her face, pistol hot in her grip. “This is too easy,” she thought, pride swelling, the gore just graphics to her—\textit{Raven’s gonna flip when I beat his ass at this.} A flicker of doubt nudged her—\textit{Kinda gory for a game}—but she shoved it down, too caught in the rush. The terminal beeped—\textit{Target: 200 meters}—and she spotted him: a figure in a tailored coat, limping toward a convoy, flanked by more guards. Putin, her “big boss,” a silhouette she’d bragged about nailing at the bar.

“Boss level time!” she yelled, lining up the shot, finger twitching on the trigger. The distance was tricky—wind howled, snow blurred her aim—but she steadied, breath hitching with glee. “Gotcha, old man,” she whispered, ready to fire, when a guard bellowed, “She’s not one of ours!” Bullets whizzed past, pinging the car’s hull, and she ducked, laughing through the shock. “Nice try, assholes!” she called, popping up to return fire—one dropped, knee exploding in a red mist, his scream cut short as he hit the ground. “Four!” she crowed, tallying like it was points, not lives.

Gunfire stitched the air—sharp, relentless—and she rolled behind a crate, snow soaking her jeans, the cold biting deep. “They’re pissed now,” she giggled, reloading with shaky hands—Raven’s shirt snagged on the crate, tearing at the hem. She peeked out, spotting Putin’s convoy revving up, taillights glowing red. “No you don’t,” she muttered, aiming again, but a bullet grazed her arm—hot, searing, a shallow line of red welling fast. “Ow, fuck!” she yelped, clapping a hand over it, blood smearing her fingers. \textit{That hurt—too real,} she thought, doubt creeping louder, but the thrill roared back—\textit{Immersion’s insane!}

She fired blind, clipping another guard—his chest burst, body twitching as he fell—and grinned, ignoring the sting. “Five—suck it!” she shouted, the chaos her playground, the blood just paint to her naive eyes. Putin’s car rolled forward, guards closing ranks, and she bolted up, chasing the thrill—\textit{Gotta nail the boss!}—snow crunching underfoot, pistol raised. A radio crackled somewhere—\textit{“Intruder, Sector 12—contain her!”}—but she took it as AI chatter, not a real cry. “Bring it on!” she yelled, darting closer, the convoy’s rumble shaking the ground.

Her heart pounded, wild and free—\textit{Bet I’d smoke Raven’s score}—the gore, the screams, all part of the ride. The terminal blinked—\textit{Threats: 2 remaining}—and she laughed, a dark edge creeping in. \textit{This is nuts,} she thought, but the fun drowned the warning—\textit{Let’s finish it.} She was a hurricane in Moscow-7, a civilian killing with glee, blind to the truth snapping shut around her.

\section{Tearing Sensation}

Sasha lined up her shot in Sector 12, snow whipping her face, the pistol’s grip slick with sweat and blood from her grazed arm. Putin’s convoy rumbled ahead, taillights glinting red through the crimson storm, guards scattering as she grinned—\textit{Boss down, game over!} Her finger tightened on the trigger, heart pounding with wild glee, when the world went black. The terminal flared—\textit{Session Terminated}—and a “tearing” sensation yanked her back, a gut-punch of static and vertigo that spun her skull. “What the hell?” she gasped, ripped from Moscow-7 mid-breath, landing sprawled in the Transatron rig.

She yanked off the headset, hands shaking as it clattered to the floor, neural plugs popping free with a sting she barely felt. Her chest heaved, breaths ragged, the apartment snapping into focus—dim, messy, the coffee mug still warm on the counter. “Holy shit,” she wheezed, stumbling to her feet, legs wobbly like a newborn colt’s. The rig’s glow faded, its hum dropping to a faint beep, and she clutched her arm—blood smeared Raven’s torn shirt, the graze a hot, throbbing line. \textit{Best game ever,} she thought, adrenaline buzzing, a grin splitting her face despite the spin.

“What cut it off?” she muttered, kicking the rig’s base, half-laughing through the confusion. “Did I win?” Her voice echoed in the empty room, the city’s hum filtering through cracked windows—steady, normal, a stark flip from the gunfire and screams. She paced, boots scuffing the floor, heart still racing—\textit{That was insane!}—the thrill drowning the ache in her arm, the faint nausea from the jump. Moscow-7 lingered in her mind—blood in the snow, Putin’s limp, guards dropping like flies—too vivid, too raw, but she chalked it up to killer tech. \textit{Raven’s a goddamn wizard.}

Her hands trembled, not from fear but the high—she flexed them, laughing, “I smoked it!” The graze stung, blood crusting, and she shrugged—\textit{Immersive as fuck, worth it.} She didn’t clock the rig’s beep speeding up, a countdown she’d missed—\textit{Lockdown Initiated}, a Consortium failsafe ticking away. Outside, boots thudded faintly, heavier now, shadows moving below the window—Liang’s team, breaching closer—but Sasha was too wired, too blind, pacing with a victor’s strut. “Gotta tell him I beat his ass,” she said, imagining his smirk, oblivious to the real hell she’d stirred.

The apartment felt smaller, the air thicker—sweat clung to her skin, Raven’s shirt sticking to her back—but she didn’t care, too pumped to sit. “Next time, I’m finishing that bastard,” she vowed, replaying Putin’s silhouette, the convoy’s roar. Doubt flickered—\textit{Why’d it hurt so much?}—but she laughed it off, a thrill-seeker’s shrug. The Transatron beeped again, sharp and final, and she glanced at it, brow furrowing—\textit{Glitchy piece of junk.} The coffee mug mocked her, still there, a lifeline to normal she didn’t grab.

Then—a thud, loud, close—boots on the stairs, a shadow at the door. Her head snapped up, pulse kicking anew, but she grinned—\textit{Raven?}—not clocking the danger until it was too late. The rig’s screen blinked—\textit{00:01:30}—unseen in her haze, the countdown ticking down to chaos. She was high on her “win,” blind to the blood on her hands, the lives she’d taken, the mercenaries about to crash through. “Best damn ride,” she breathed, exhilarated, confused, teetering on the edge of a reality she didn’t yet grasp.

\chapter{Urgent Flash}
\section{Crumbling Block}

Liang Wei stood under the flickering streetlamp outside the crumbling apartment block, night cloaking the chipped facade in shadow. The cold bit through his dark camo and body armor, but his focus was steel—Beijing’s orders burned in his skull: Get the secrets, no excuses. His team—five operatives in masks, silenced pistols drawn—stacked silently at the door, breaths steady, poised. He didn’t know who was inside, didn’t care—just that the machine was here, humming with the intel they needed. With a sharp two-finger jab, he signaled the breach.

The door splintered under a boot’s crash, wood cracking loud in the empty street. They surged in, boots grinding glass into the floor, the air thick with stale coffee and sweat. Liang’s eyes snapped to the corner—a hulking rig, lights pulsing red, cables snaking wild—and a figure tangled in it, sprawled like she’d been caught mid-fight. A woman—hair a mess, shirt torn—groaned as the neural plugs tore free with a wet snap, her hands flailing weak. His men hauled her up, pinning her arms, zip-tying her wrists tight as she yelped, blood trickling from her lip—fresh, raw, like she’d just been hit.

“Target live,” Liang barked, voice cutting the haze. His team shoved her against the wall, her gasps ragged as she blinked, dazed. Liang stepped closer, scarred face catching the rig’s glow. Operator, he thought, gut tightening—caught her red-handed, strapped into the damn thing. Beijing wanted the machine’s secrets—codes, data, whatever “numbers” the briefings whispered about—and she was the key. “Secure the room,” he ordered, his men fanning out, weapons sweeping shadows.

The apartment was a wreck—gear scattered, the rig’s hum needling the air, its lights strobing fast. He ignored it—tech wasn’t his problem, she was. “Who are you?” he demanded, cold as his pistol’s steel, but she stammered, “W-what? Who are you?”—voice shaky, eyes darting. Playing dumb, he sneered inwardly, stepping closer, gloved hand seizing her chin. “The numbers. You pulled them from him—where are they?” Confusion twisted her face, her breath hitching. “I don’t know anything—please!”

Liang’s jaw tightened—Lying bitch. No one sat in that machine by accident. Beijing’s clock ticked, and he wasn’t leaving empty-handed. He nodded to Chen, his wiry second, who cracked his knuckles, stepping up. “You’ll talk,” Liang said, voice flat, releasing her chin. The rig’s whine spiked—irritating, irrelevant—but his focus stayed locked. She’s got them, he thought, certainty a vice on his mind. We’ll rip it out. The air thickened—boots shifted, ozone stung his nose—and his earpiece buzzed: Security’s closing. Hurry. He didn’t flinch. She’d break, or she’d bleed—Beijing didn’t care which.

\section{Chipped Sink}

Liang Wei loomed over Sasha in the apartment’s cramped kitchenette, her zip-tied wrists chafing red against a rickety chair they’d shoved her into. The table was kicked aside, leaving her exposed under the Transatron’s eerie glow, its hum a low drone beneath the tension. His team fanned out—Chen at his side, the others guarding the door and windows, their silenced pistols glinting in the dim light. Liang slammed a gloved fist on the counter, the crack sharp as a gunshot. “The numbers—where are they?” he demanded, voice cold, each word a blade aimed at her defiance.

Sasha’s head jerked up, blood trickling from her split lip, eyes wide with terror and confusion. “What numbers? It’s a game—I swear!” she stammered, voice cracking, her borrowed shirt—Raven’s, Liang guessed—clinging to her sweat-soaked frame. He snarled, leaning in close, his scarred face inches from hers. “Bullshit. You jumped—you’re an operator.” Her naivety stank of a lie; no civilian stumbled into a Dimensional Transatron and lived to play dumb. Beijing’s orders burned in his skull—*Extract or eliminate*—and time was bleeding out.

Chen stepped forward, knuckles popping, his lean frame coiled with menace. Liang gave a curt nod—unspoken permission—and Chen’s backhand snapped across Sasha’s face, a wet smack that split her lip wider. Blood sprayed, dotting her shirt, and she gasped, head lolling. “I don’t know anything!” she cried, tears mixing with the red, her voice raw and desperate. Liang’s eyes narrowed—\textit{She’s good,} he thought, irritation flaring. \textit{Too good.} He’d broken tougher shells than this, and Beijing’s clock ticked louder with every wasted breath.

“Again,” Liang said, voice flat, stepping back to let Chen work. The mercenary grabbed her hair, yanking her head up, and slapped her again—harder, the sound echoing off the walls. Her cheek swelled, a bruise blooming fast, and she sobbed, “Please, stop—I don’t!” Liang crouched, leveling his gaze with hers, his pistol resting heavy in its holster. “Putin’s codes. In your head. Give them up,” he said, slow and deliberate, watching for the crack. Her sobs hitched, eyes darting like a trapped animal’s. “I don’t—I swear!” she choked out, spit flecking her chin.

The Transatron’s whine crept into the air—low, insistent, a distraction Liang dismissed with a flick of his hand. “Tech glitch,” he muttered to Chen, focus unwavering. \textit{She’ll crack,} he told himself, though doubt flickered—\textit{Or she’s collateral. Fuck, we can’t afford mistakes.} Beijing’s voice echoed in his mind—*Results, Liang, or your head*—and stress clawed his gut. He’d seen ops go south, seen men die for less, but this? This was a razor’s edge, and Sasha was the key—or a dead end. “Last chance,” he warned, standing, his shadow swallowing her. “Talk, or we carve it out.”

Her sobs filled the room, broken and pitiful, but no answers came—just pleas, raw and useless. The air thickened—blood, sweat, the faint ozone from the rig—and Liang’s patience thinned. His team shifted, restless, the silence outside too heavy, too still. \textit{Time’s slipping,} he thought, urgency spiking. Chen cracked his knuckles again, ready, and Liang nodded—escalation was the only play left. The numbers were here, buried in her skull or not, and he’d rip them free, one scream at a time.

\section{Shallow Line}

Liang Wei paced the kitchenette, Sasha’s sobs a grating rhythm against the Transatron’s rising whine—sharp now, cutting through the apartment’s stifling air. She slumped in the chair, zip-ties biting her wrists, blood smearing Raven’s torn shirt from her split lip and swollen cheek. The table lay overturned, a casualty of Chen’s last blow, and the floor glistened with sweat and red streaks. Liang’s team held their posts—guns trained on the door, windows, shadows—tension coiling tight as the rig’s red lights pulsed faster, a heartbeat he still dismissed. \textit{Tech’s nothing—focus,} he thought, but the sound gnawed at him, a splinter under his skin.

“Break her,” Liang ordered, voice flat, nodding to Chen. The wiry mercenary stepped up, drawing a knife from his belt—short, serrated, glinting under the dim bulb. He grabbed Sasha’s arm, pinning it to the chair, and sliced a shallow line down her forearm—slow, deliberate, blood welling fast as she screamed, “Please, stop!” The sound tore through the room, raw and jagged, her body jerking against the ties. Liang crouched, face inches from hers, watching her eyes—wild, wet, pleading. “Putin’s codes,” he said, slow and cold. “In your head. Give them up.” She sobbed, “I don’t—I don’t know anything!”—spit and tears mixing with the blood dripping to the floor.

Chen yanked her head back by the hair, exposing her throat, and Liang waved him on—escalation was the play. “Water,” he snapped, and a merc hauled a bucket from the sink, sloshing cold over the edge. Chen dragged her to the basin, shoving her face under the faucet—water gushed, her nose bubbling as she thrashed, legs kicking, muffled screams gurgling up. Liang counted—ten seconds, twenty—then nodded; Chen pulled her back, gasping, choking, water streaming down her face, soaking her shirt to her skin. “The numbers,” Liang pressed, voice a steel thread, “now.” She coughed, retching, “I swear—I don’t!”—her voice a broken rasp, eyes darting like a cornered animal’s.

The Transatron’s whine crescendoed, red lights flashing urgent—a warning Liang barely clocked, too locked on her. \textit{She’ll crack,} he told himself, stress clawing his gut. \textit{They always do.} Beijing’s shadow loomed—\textit{Results, Liang, or you’re done}—and every second she held out was a noose tightening. He’d tortured before—rebels, spies, harder bastards than this—but her pleas rang hollow, too raw. Doubt flickered—\textit{What if she’s nothing?}—but he crushed it, pragmatism overriding. “Again,” he said, standing, and Chen dunked her once more—longer this time, her thrashing weaker, bubbles slowing as she drowned in inches.

He pulled her up, hair plastered, face pale, coughing water in ragged bursts. “Talk!” Liang barked, slamming a fist on the counter—wood splintered, his glove flecking red from her blood. She wheezed, “I don’t know—please!”—and Chen backhanded her, a wet smack that snapped her head sideways, a fresh bruise blooming fast. The rig’s beeping pierced through—faster, insistent—and Liang glared at it, irritation spiking. “Shut that shit up,” he muttered, but no one moved—focus stayed on her, the key he couldn’t turn.

Blood pooled under her chair, mixing with water—her arm bled steady, lip split wide, eyes swelling shut. \textit{Time’s slipping,} he thought, urgency a vice on his chest. Beijing wanted the numbers—Putin’s secrets, Consortium’s prize—and he was running dry. “Last chance,” he growled, drawing his pistol, pressing the cold barrel to her temple. She flinched, sobbing, “I don’t—I don’t!”—and he held it there, finger twitching, weighing her life against his orders. \textit{She’s collateral,} the doubt whispered, louder now, but Beijing’s voice drowned it—\textit{No mistakes.}

The Transatron’s screen flickered—\textit{00:05:00}—a countdown he didn’t see, too deep in the mess. Chen cracked his knuckles, ready for more, and Liang nodded—\textit{One last push.} The room choked with her cries, the rig’s whine, his team’s silence—violence thick as the blood on the floor. He’d get the numbers, or she’d die trying, and Beijing wouldn’t care which.

\section{Spiked Whine}

Liang Wei paced beside Sasha, her slumped form a wreck in the chair—blood dripping from her sliced arm, water pooling at her feet, sobs fading to weak gasps. The kitchenette was a slaughterhouse—overturned furniture, red smears on the floor, the air thick with sweat and copper. His team held their ground, guns up, shadows stretching long under the Transatron’s pulsing red glow. The rig’s whine had spiked—loud, jagged, a drill in his skull—and its console flashed urgent, lights strobing like a warning flare. \textit{Machine’s a problem,} he thought, irritation spiking, but he shoved it aside—Sasha was the priority.

“What’s that shit doing?” Zhang muttered, stocky frame tense as he glanced at the rig, pistol twitching toward it. Liang snapped, “Ignore it—probably rebooting,” his voice a whip cracking through the haze. Chen pressed Sasha harder, fist cocked—“Numbers, now!”—but her head lolled, eyes half-shut, voice a broken croak: “I don’t know!” Blood streaked her face, her shirt soaked—Raven’s, torn and useless—and Liang’s patience frayed thin. \textit{She’s wasting my fucking time,} he seethed, Beijing’s orders a noose—\textit{Extract or end it.}

The Transatron’s screen glitched—\textit{Lockdown Initiated}—text flickering fast, but Liang’s focus stayed locked on her, missing the shift. The beeping accelerated—sharp, relentless—and Zhang shifted, uneasy. “Boss, that’s no reboot,” he said, voice low, but Liang waved him off, sweat beading on his scarred brow. “Focus!” he barked, stepping closer to Sasha, pistol drawn now, barrel hovering near her temple. Her sobs hitched, a whimper escaping—“Please…”—but no numbers came, just pleas he’d heard too many times. \textit{She’s nothing,} doubt clawed louder, but he crushed it—\textit{Beijing doesn’t take excuses.}

Chen grabbed her hair, yanking her upright, and she cried out—weak, fading fast. “One more,” Liang growled, nodding, and Chen’s fist slammed her jaw, a wet crunch as her head snapped back. Blood sprayed, a tooth skittering across the floor, and she sagged, coughing red. The rig’s whine hit a fever pitch—lights flashing wild, a countdown ticking unseen: \textit{00:02:00}. “Shut it down!” Zhang yelled, stepping toward it, but Liang grabbed his arm, shoving him back. “She’s the mission—deal with her!” His voice cracked, control slipping, the noise a hammer on his nerves.

The apartment trembled—vibrations from the rig, subtle but growing, rattling the walls. Sasha’s eyes fluttered, barely conscious, blood pooling under her chair—her arm a mess, her face a ruin. \textit{We’re out of moves,} Liang thought, panic edging in, Beijing’s shadow choking him. His earpiece crackled: “Security’s four minutes out—move!” The Consortium was closing in—Kessler, maybe, some bastard enforcer—and the rig’s chaos was a ticking bomb he couldn’t ignore. “Fuck,” he rasped, wiping sweat from his eyes, pistol trembling slightly in his grip.

Chen stood ready, knife red with her blood, but Liang held up a hand—\textit{Wait.} The Transatron’s threat loomed, a beast waking up, and he glared at it, mind racing. \textit{This op’s fucked,} he admitted, the realization bitter. Sasha wasn’t breaking—no numbers, no win—and the machine was turning on them. “Positions,” he snapped, voice taut, his team scrambling—guns up, eyes darting. The rig beeped louder—\textit{00:01:45}—unseen but screaming, and Liang’s grip tightened, a soldier cornered in a war he hadn’t planned.

\section{Hard Raps}

Liang Wei stood over Sasha’s broken form, the apartment a pressure cooker—blood and water slicked the floor, the Transatron’s beeping a relentless pulse hammering his skull. She hung limp in the chair, zip-ties cutting into her swollen wrists, her face a mess of bruises and red, breaths shallow and ragged. The rig’s red lights strobed wild, its whine a banshee scream—\textit{00:01:30} ticking down unseen on the screen—and the walls vibrated, a low rumble shaking dust from the ceiling. His team braced—Chen at Sasha’s side, knife dripping, Zhang and the others with guns trained on the door, shadows twitching in the dark.

A sharp knock rattled the frame—three hard raps, deliberate, cutting through the chaos. Liang froze, pistol snapping up, his scarred face taut with sweat. “Security or a trap?” he rasped, voice low, mind racing—\textit{Either way, we’re fucked.} His earpiece had warned of Consortium forces, four minutes out, but this was too soon—Kessler, maybe, some bastard enforcer sniffing their mess. Sasha stirred, a weak groan escaping her split lips, and Liang shoved his pistol into her spine, the cold barrel digging in. “Answer it,” he hissed, “Fuck this up, you’re dead.” She flinched, tears mixing with blood, hands trembling as he cut her ties—fingers too numb to resist.

She stumbled to the door, legs buckling, Liang’s gun a shadow at her back. His team scattered—Zhang ducked behind the couch, Chen pressed to the wall, pistols silent but ready. The rig’s countdown pulsed—\textit{00:01:15}—unnoticed in the haze, its whine drowning her sobs. “Move!” Liang snapped, shoving her forward, her bare feet slipping on the wet floor. She reached the knob, breath hitching, the barrel’s chill a death promise against her skin. “Who’s there?” she croaked, voice a ghost, but the knock came again—harder, insistent—no answer, just weight behind it.

Liang’s pulse thundered—\textit{Time’s gone,} he thought, panic clawing his chest. Beijing’s orders—\textit{numbers or nothing}—crumbled here, Sasha a useless wreck, the rig a bomb he couldn’t defuse. “Open it,” he growled, finger twitching on the trigger, and she turned the knob, slow, trembling, the door creaking wide. Shadows loomed outside—boots, a trench coat, a glint of metal—but Liang didn’t see, too locked on her, on the exit she might buy him. “Positions—now!” he barked, voice cracking, his men tightening their grip, the room a killbox primed to blow.

The air choked—blood, ozone, her fear—and the Transatron’s beeping hit a fever pitch—\textit{00:01:00}—vibrations rattling the floor, a death knell he couldn’t ignore. Sasha swayed, tears streaming, her hand slipping off the knob as the figure stepped closer—Kessler, he’d bet, come to clean up. “She’s our ticket out,” he rasped to Chen, shoving her forward, a shield for whatever walked in. The rig’s screen flashed—\textit{00:00:55}—unseen, unstoppable, and Liang’s grip tightened, a soldier cornered, betting on blood to save his skin.

“This op’s fucked,” he admitted, bitter and raw, the knock still echoing in his skull. Sasha’s doom hung heavy—expendable, broken—and he’d use it, Beijing be damned. The door gaped, the figure’s shadow swallowing the light, and Liang braced—gun up, breath held—for the storm about to crash through.

\chapter{Tidal Roar}

\section{Cracked Pavement}

Kessler Hahn pulled his unmarked sedan to a stop outside the apartment block, snow dusting the cracked pavement under a flickering streetlamp. The night bit cold, wind tugging his trench coat as he stepped out, Consortium badge glinting under his vest. His Glock sat heavy, a steady weight, and he checked his wrist device—a ping: Asset Breach Detected: Operator Unknown. “Priority one,” he muttered, boots crunching toward the shadowed stairwell. The city’s hum was too quiet—trouble’s live, his gut warned, sharpened by years of stomping out messes.

The device blinked—Lockdown Active—and Kessler’s eyes narrowed, scanning the windows. The rig was up there, Consortium property, humming with something gone wrong—someone had touched it, someone not cleared. Operator Unknown, he thought, jaw tight. Could be Raven screwing around, a thief, or worse—outsiders sniffing around. He’d seen breaches before—gear fried, bodies broken—but this felt off, sharp-edged. The Consortium didn’t play loose with its toys, and he was the fix. He climbed the stairs, steps thudding, hand on his gun.

At the door—scarred, peeling—he paused, ears pricked. A faint thud inside, then silence—too heavy, he thought, unease prickling. He knocked hard—three raps, loud, official. “Consortium Security. Open up,” he called, voice steady, slicing the cold. No answer—just that quiet, thick as a held breath. His device hummed—Anomaly Escalating—and he frowned, snow flaking off. Raven’s file flickered in mind—gritty, loyal, fraying—Hope it’s not him, but the breach screamed trouble, and Kessler didn’t bank on hope.

He scanned the frame—no blood, no break-in marks—but the air felt charged, wrong. Late-night breach? he mused, caution spiking. The Consortium locked its gear tight—codes, failsafes—and a blip like this meant a leak or a corpse. He’d cleaned both—thieves gutted, tech torched—and this place stank of it. His gloved hand flexed—Move fast if it’s hot. Another knock—harder—and he listened, breath fogging. A shuffle, faint, then nothing. Someone’s there, he thought, ticking through options—Raven, a squatter, or a hunter after something big. The device pinged—00:01:00—a countdown he didn’t see, but his gut felt it. Live wire, he decided, boots planted, ready to breach if the next knock failed.

\section{Split Lip}

Kessler Hahn stood at Raven’s door, the third knock unanswered, the silence inside thick as the snow outside. His wrist device buzzed—\textit{Lockdown Active: 00:01:00}—a countdown he didn’t see but felt, the air heavy with wrongness. He drew his Glock, gloved hand steady, and pushed the door—it creaked open, unlatched, framing a battered figure in the dim light. A woman—Sasha Volkov, Raven’s fling, per the dossier—staggered there, bloodied and bruised, her face swollen, lip split, hands trembling. \textit{Everything okay?} he started to say, but her state screamed no—\textit{Beaten, not jumped,} he clocked, instinct flaring.

“Everything okay?” he asked anyway, voice low, eyes scanning past her—shadows shifted, boots scuffed faintly. She croaked, “Yeah, glitch,” her gaze darting, a lie so thin it stank. Kessler stepped closer, Glock low but ready. “Clearance code,” he pressed, testing—Consortium protocol, not a question. She fumbled—“Uh, blue… five?”—wrong, dead wrong, and his gut twisted—\textit{She’s no operator.} “I’m coming in,” he said, foot crossing the threshold, when a gunshot cracked—sharp, deafening. Her head jerked, red mist sprayed, and she crumpled, a bullet through her skull, blood splattering his trench coat.

Kessler dove behind the wall, Glock up, heart slamming—\textit{Ambush,} his mind snapped, the shot’s muzzle flash flaring from the dark. “Fuck,” he rasped, plaster dust kicking up as bullets chewed the frame—fast, disciplined, not panicked. Sasha’s body hit the floor, eyes blank, blood pooling fast—\textit{Civilian caught in this shit,} he thought, no time for pity. He peeked, saw movement—black gear, silenced pistols—\textit{Outsiders,} he pegged, Chinese maybe, hunting the numbers. The Transatron’s glow pulsed inside, red and urgent, its whine rising—\textit{00:00:50}—a death clock he hadn’t clocked yet.

“Consortium Security—stand down!” he barked, a formality they’d ignore, and they did—gunfire answered, stitching the wall, forcing him low. He rolled inside, using the couch as cover, Glock barking twice—blind shots, a grunt replied, a merc down somewhere in the haze. \textit{Two at the door, one flanking,} he counted, breath fogging, the room a wreck—overturned furniture, blood slicking the floor. Sasha’s death was a flare—\textit{They’re desperate,} he thought, adrenaline a steel thread through his veins. \textit{Numbers or bust.}

The air bit with gunpowder, sharp and thick—\textit{Seen this shit before,} he told himself, weariness warring with focus, \textit{just not this fucked.} His coat snagged on glass, blood from Sasha staining the hem, and he cursed under his breath—\textit{Move fast or die.} The Transatron beeped louder—\textit{00:00:45}—a sound he caught now, gut twisting—\textit{Self-destruct?}—but the fight was live, no time to check. Liang’s voice cut through, cold and sharp—“Flank him!”—and Kessler braced, the firefight erupting full tilt, a storm he’d ride or break on.

\section{Exploding Plaster}

Kessler Hahn rolled into Raven’s apartment, the couch his shield as bullets ripped through the doorway, plaster exploding in white bursts around him. The air bit with gunpowder, sharp and acrid, Sasha’s body still warm on the floor—headshot, red mist staining his coat from the breach. His Glock barked twice—blind shots into the dark—and a grunt answered, a merc dropping with a wet thud, blood pooling fast. \textit{Two at the door, one flanking,} he counted, pulse hammering, eyes scanning the wrecked space—overturned furniture, shadows darting, the Transatron’s red glow strobing like a death knell.

He popped up, Glock steady—two rounds cracked, surgical, and Chen’s jaw shattered, teeth and blood spraying as he crumpled, his knife clattering uselessly. Liang’s voice cut through, cold and sharp: “Flank him!” A merc charged from the kitchenette—big, fast, blade gleaming—Kessler ducked the swing, grabbed the wrist, snapped it with a crack, and pumped two into his chest. The body hit the floor, twitching, red leaking wide, and Kessler dove back behind the couch, bullets chewing the upholstery—stuffing flew, a storm of chaos in the cramped killbox.

“Three left, maybe four,” he muttered, breath fogging, ears ringing from the gunfire’s roar. Glass crunched underfoot as he shifted, Glock hot in his grip—\textit{Disciplined bastards,} he thought, clocking their moves. \textit{Not Consortium—outsiders.} Chinese, likely, hunting the numbers, and he’d walked right into their shitshow. A shadow loomed—Zhang, stocky, pistol blazing—and Kessler rolled, firing back—two shots missed, the third grazed Zhang’s arm, a hiss of pain as he ducked behind the sink. The Transatron beeped louder—\textit{00:00:45}—a shrill warning Kessler spotted mid-fight, his gut twisting. \textit{Fuck—self-destruct.}

Gunfire stitched the air—sharp, relentless—plaster dust choking his lungs as he traded shots. Zhang’s head popped up, and Kessler nailed him—round through the throat, a gurgle as he slumped, blood jetting over the counter. “Two down,” he rasped, reloading fast, the mag clicking home. Liang fired back, a burst shredding the couch’s arm—Kessler ducked low, shrapnel stinging his cheek, hot and wet. “Machine’s gonna blow, idiots!” he yelled, voice raw, hoping to spook them, but Liang’s silence was answer enough—\textit{He’s in deep,} Kessler thought, focus sharpening. \textit{Clear the room, then the rig.}

A merc lunged from the shadows—fast, silent, pistol spitting—and Kessler took a graze to the arm, fabric tearing, blood seeping warm. He pivoted, snapped off a shot—center mass, the guy dropped, chest a ruin, twitching once before stilling. “Three,” he growled, pain flaring but ignored, adrenaline a steel thread through his veins. The apartment shook—vibrations from the Transatron, its countdown screaming—\textit{00:00:30}—and Kessler glimpsed Liang, scarred face taut, retreating toward the kitchenette, gun up. \textit{Leader’s mine,} he vowed, rolling to new cover—a splintered table—bullets pinging off its edge.

The rig’s red lights flashed wild, a death clock he couldn’t unsee—\textit{Outgunned, but they’re rattled,} he calculated, counting shots, their rhythm faltering. He fired blind—two cracks—and heard a curse, a body hitting the wall. “Four,” he rasped, chest tight, the air a cacophony—thumping gunfire, cracking wood, the Transatron’s wail. Sasha’s blood slicked the floor, her blank eyes a ghost in his peripheral—\textit{Civilian or operator, dead either way,} he thought, focus cold, no room for guilt. Liang’s shadow moved—\textit{Last stand}—and Kessler braced, Glock steady, the fight a razor’s edge with seconds ticking down.

\section{Screaming Beep}

Kessler Hahn ducked behind the splintered table, Sasha’s blood slick under his boots, the apartment a warzone of shattered glass and bullet-pocked walls. The Transatron’s beeping screamed—\textit{00:00:30}—its red lights flashing wild, vibrations rattling the floor as the self-destruct countdown bore down. Liang’s last merc traded shots from the kitchenette, pistol spitting—Kessler fired back, a round bursting Zhang’s throat, blood jetting as he gurgled down, painting the sink red. “Four,” Kessler rasped, voice raw, reloading fast—Glock hot, mag clicking home—but the fight wasn’t done.

The front door banged open—boots pounded in, three more mercs, fresh and armed, their dark camo stark against the chaos. “Fuck me,” Kessler growled, arm grazed and bleeding from the last volley, the sting hot under his torn sleeve. Bullets hammered the table—wood splintered, shrapnel nicking his cheek—and he rolled to new cover, a toppled chair, chest tight with adrenaline and dread. \textit{Outnumbered, outgunned,} he thought, counting—\textit{Five total now, maybe six.} The rig’s whine hit a fever pitch—\textit{00:00:20}—a death knell he couldn’t dodge, the room shaking like a beast waking up.

“Machine’s gonna blow!” Kessler yelled again, voice hoarse, hoping to spook them, but the new mercs fanned out—disciplined, silent—ignoring the rig, eyes on him. Liang fired from the kitchenette, a burst shredding the chair’s back—Kessler ducked, plaster dust choking his lungs, and snapped off two shots—one missed, the other clipped a merc’s shoulder, a hiss of pain as he ducked behind the couch. \textit{Chinese bastards,} he pegged, their gear too crisp for rogues—\textit{Beijing’s dogs, hunting the numbers.} The Consortium’s prize was slipping, and he was the last line.

A merc charged—fast, rifle up—Kessler dove, tackling low, slamming him into the wall with a crunch. The rifle barked, wild shots pocking the ceiling, and Kessler drove an elbow into his windpipe—cartilage snapped, a choked gasp as the guy dropped, twitching. “Five,” he grunted, snatching the rifle—Consortium didn’t train for mercy—and swung it up, firing a burst—another merc’s chest exploded, blood spraying as he staggered back, dead before he hit the floor. “Six,” Kessler rasped, but the table took a rocket hit—fireball roared, heat searing his face, hurling him sideways into the wall.

His ears rang, vision swimming—\textit{Too many, too fast,} he thought, scrambling to his knees, coat singed, blood dripping from a shrapnel graze on his leg. The Transatron’s screen flashed—\textit{00:00:10}—and Liang’s voice cut through, strained: “Finish him!” A merc loomed—pistol raised—and Kessler fired first, round punching through his eye, brain matter splattering the rig. “Seven,” he coughed, smoke burning his lungs, but Liang bolted toward the kitchenette’s garage exit—\textit{Running,} Kessler clocked, rage flaring. \textit{Not yet, bastard.}

The rig’s vibrations shook the floor—\textit{00:00:05}—and Kessler staggered up, Glock in one hand, stolen rifle in the other. “Get to the garage!” he rasped, mind racing—\textit{Now or never.} Liang’s earpiece crackled—\textit{“Numbers secure—pull out!”}—a lie or a win, Kessler couldn’t tell, but it fueled him. He lunged for the kitchenette door, a merc’s body blocking—kicked it aside, blood slicking his boots—and glimpsed Liang vanishing into the dark. The Transatron hit zero—\textit{00:00:00}—a deafening roar erupted, heat blasting his back as the explosion tore through, a wall of fire and debris chasing him out.

\section{Raining Debris}

Kessler Hahn bolted through the kitchenette’s garage door, the Transatron’s roar a tidal wave at his back—\textit{00:00:00}, zeroed out, the self-destruct igniting. A merc lunged from the shadows—last ditch, desperate—and Kessler slammed an elbow into his windpipe, a choked gurgle as he dropped. No time—\textit{Move!}—he kicked a shelf aside, crashing it down on the body, and dove for the beat-up sedan parked in the dim garage. No keys—\textit{Fuck it}—he hit the floor as the explosion erupted, a deafening blast of heat and force hurling him into the car’s side.

The world shattered—flames devoured the apartment, walls collapsing in a thunder of brick and steel, the rig’s core a fireball that lit the night orange. Debris rained—jagged chunks of concrete, twisted metal—smashing the garage roof, buckling it with a groan. Kessler coughed, smoke searing his lungs, ears ringing as he crawled from the wreck, coat singed, blood streaking his face from a shrapnel graze. \textit{Close,} he thought, chest heaving, \textit{too fucking close.} The sedan’s frame shielded him—dented, glass blown out—but alive by inches, the heat still licking his back.

He staggered up, Glock dangling, the garage a smoldering cave—flames hissed against snow drifting through the breached roof, the air thick with ash and ozone. Liang was gone—slipped into the night, a shadow with maybe the numbers, maybe nothing. \textit{Bastard got out,} Kessler rasped, spitting blood into the rubble, the fight’s toll sinking in—arm grazed, leg stinging, every breath a knife. Sasha’s blank eyes flashed in his mind—\textit{Civilian, dead for this shit}—and the mercs, shredded or fled, a trail of bodies he’d carved through.

The Transatron’s husk smoked in the wreckage, its glow snuffed, cables melted into slag—\textit{Consortium’s failsafe,} he thought, bitter. No evidence left, no numbers, just a crater where answers might’ve been. \textit{What were they after?} he wondered, questions burning hotter than the flames—\textit{Numbers, sure, but why her?} He wiped sweat and blood from his eyes, the city’s hum creeping back, a distant pulse under the ringing silence. Liang’s earpiece crack—\textit{“Numbers secure”}—echoed, a taunt he couldn’t pin—truth or bluff, it gnawed at him.

He rasped into his radio, voice a gravelly wreck: “Threat neutralized. Send backup—now.” Static answered, then a faint “Copy,” the Consortium’s wheels turning slow as ever. Kessler sank against the sedan, Glock across his lap, watching the fire die—snow hissed on embers, the garage a tomb for the night’s slaughter. \textit{Seven down, one ran,} he tallied, the count a hollow win—Sasha gone, Raven’s rig ash, the numbers a ghost slipping through his fingers.

His breath steadied, frost biting his lungs, the adrenaline crash leaving him raw. \textit{Hunt’s not over,} he vowed, jaw clenching—Liang was out there, and the Consortium would demand blood, answers, something. He’d deliver, or die trying—duty, not heroics, the chain that kept him moving. The faint hum of a Consortium craft pierced the night—backup, late as hell—and Kessler stood, wincing, coat heavy with blood and soot. The wreckage smoldered, a question mark in the snow, and he turned to face the dawn, a survivor with a war still burning.

\end{document}